---
title: "bootstrapping"
author: "Chen Liang"
date: "2023-11-16"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
set.seed(1)

```


```{r}
n_samp=250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const |> 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)

sim_df_nonconst |>
  ggplot(aes(x=x,y=y))+
  geom_point()

```

fit some linear models
```{r}
sim_df_const |>
  lm(y~x,data=_) |>
  broom::tidy() |> 
  knitr::kable(digits = 3)
```

# Draw and analyze a bootstrap sample

start with a lil function
```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
```

see how this work
```{r}
boot_sample(sim_df_nonconst) |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

## Draw a lot of samples and analyse them
```{r}
boot_straps = 
  tibble(strap_number = 1:1000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = sim_df_nonconst))
  )

boot_straps |> 
  slice(1:3) |> 
  mutate(strap_sample = map(strap_sample, arrange, x)) |> 
  pull(strap_sample)
```

let's do the `lm` fit
```{r}
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(y ~ x, data = df) ),
    results = map(models, broom::tidy)) |> 
  select(-strap_sample, -models) |> 
  unnest(results) 
```

summarize these results
```{r}
bootstrap_results |> 
  group_by(term) |> 
  summarize(boot_se = sd(estimate)) |> 
  knitr::kable(digits = 3)
```

look at the distribution
```{r}
bootstrap_results |> 
  filter(term== "x") |>
  ggplot(aes(x=estimate))
  geom_density()
```

can I construct a CI
```{r} 
bootstrap_results |> 
  group_by(term) |> 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```

```{r}
boot_straps |> 
  unnest(strap_sample) |> 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```

##Airbnb
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  drop_na(price, stars) |> 
  select(price, stars, borough, neighborhood, room_type)
```

let's fit a regession of `price` on other variables and look at residuals

```{r}
airbnb_fit =
  nyc_airbnb |>
  lm(price~stars+room_type+borough, data=_ )
```

```{r}
nyc_airbnb |>
  modelr::add_residuals(airbnb_fit) |>
  ggplot(aes(x=stars,y=resid))+
  geom_point()
```

rum abootstrap on this whole thing to get estimates for the effect of `stars` on `price`

```{r}
manhattan_df=
  nyc_airbnb |>
  filter(borough == "Manhattan")
  
boot_result =
  tibble(strap_number =1:1000) |>
  mutate(
    strap_sample =map(strap_number,\(i)boot_sample(manhattan_df)),
    models = map(strap_sample, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)
  )|>
  select(strap_number, results) |> 
  unnest(results) 

# boot_results |>
#  filter(term == "stars") |> 
#  ggplot(aes(x = estimate)) + 
#  geom_density()
```

```{r}
nyc_airbnb |> 
  filter(borough == "Manhattan") |> 
  modelr::bootstrap(n = 1000) |> 
  mutate(
    models = map(strap, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)) |> 
  select(results) |> 
  unnest(results) |> 
  filter(term == "stars") |> 
  ggplot(aes(x = estimate)) + geom_density()
```
